Practical Open-Loop Optimistic Planning

### 2019-06-25 paper/poster/poster.tex
Updates from Overleaf

We consider the optimal control of an MDP $\cM = (\cS, cA, R, T, \gamma)$ with bounded rewards $R$
\begin{itemize}
    \item $R$ and $T$ are \hlr{unknown}
    \item Access to a \hlb{generative model} $s' \sim \probability{s'|s,a}$ and $r\sim\probability{r|s, a}$
    \item \hlr{Fixed-budget} setting: the generative model can be queried $n$ times
\end{itemize}
}

@@

Split the budget $n$ into $M$ sequences of length $L$.
%Let $M$ be the largest integer such that $M \log M/(2 \log 1/\gamma) \leq n$\;
%Let $L = \log M / (2 \log 1/\gamma)$\;

@@

Overly pessimistic, especially in the low-budget regime.

>>>>

We consider the optimal control of an MDP $\cM = (\cS, cA, R, T, \gamma)$ with bounded rewards $R$
\begin{itemize}[nolistsep]
    \item[\incarrow] $R$ and $T$ are \hlr{unknown}
    \item[\incarrow] Access to a \hlb{generative model} $s' \sim \probability{s'|s,a}$ and $r\sim\probability{r|s, a}$
    \item[\incarrow] \hlr{Fixed-budget} setting: the generative model is \hlr{costly}, can only be queried $n$ times
\end{itemize}
}

@@

\begin{center}
    \hlb{Optimism in the Face of Uncertainty}\\
    \incarrow~ in \hlr{observed} and \hlr{future} rewards

\end{center}
%Split the budget $n$ into $M$ sequences of length $L$.
%Let $M$ be the largest integer such that $M \log M/(2 \log 1/\gamma) \leq n$\;
%Let $L = \log M / (2 \log 1/\gamma)$\;

@@

\hlr{Overly pessimistic}, especially in the low-budget regime.
